\documentclass{workreport}

\title{
    Determining Relative Distance Between Radical Spin Labels
    In Model Biological Membranes
}

\author{Michal Kononenko}
\studentnumber{20510469}
\studentid{mkononen}
\previousterm{2B}

\university{University of Waterloo}
\faculty{Engineering}
\program{Nanotechnology Engineering}
\programdirector{Shirley Tang}
\universityaddress{
    200 University Ave. West \\
    Waterloo, ON \\
    N2L 3G1
}

\employername{Institute for Quantum Computing}
\employeraddress{
    200 University Ave. West \\
    Waterloo, ON \\
    N2L 3G1
}

\begin{document}

\maketitlepage

\begin{letter_of_submittal}{Dear Dr. Tang:}{Sincerely,}

	This report, titled "Determining Relative Distance Between Radical Spin Labels in Model Biological Membranes" was prepared as my 2B work term report, in accordance with the requirements of the WKRPT 300 course. The purpose of this report is to describe a new method for determining the distance between two electrons in a biological membrane, to be used for determining the tertiary structure of membrane proteins.
	
	The Institute for Quantum Computing is a large research institute based out of the University of Waterloo, whose multidisciplinary research groups are tasked with understanding the nature of quantum information and using quantum properties to develop novel devices. The David Cory research group focuses on using spin resonance as a way to extract meaningful information out of quantum systems.
	
	I would like to thank Dr. Troy Borneman for leading this project, as well as for his valuable advice in researching and developing this method. I would also like to thank Madelaine Liddy, MSc, BASc, for providing project management as well as instruction and advice on use of laboratory equipment. I would also like to thank Rahul Deshpande for developing and optimizing the Double Electron-Electron Resonance (DEER) pulse sequences in conjunction with Dr. Borneman, that were used in the experiments. I would also like to thank Dr. David G. Cory for organizing the research group. Without his decades of invaluable experience in experimental spin physics and quantum computing, this project would not have been possible. Lastly, I would like to thank my fellow co-ops in the Cory group, who contributed greatly to the project, as well as provided a supportive, productive working environment.
	
	I hereby confirm that I have received no other help on this work excepting the contributors listed above in writing this report. I also confirm that this report has not been previously submitted for academic credit at this or any other academic institution.
	
\end{letter_of_submittal}

\toctree


\end{document}
